---
output: github_document
bibliography: ./inst/REFERENCES.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# hdme
<!-- badges: start -->
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/hdme)](https://cran.r-project.org/package=hdme)
[![Build Status](https://travis-ci.org/osorensen/hdme.svg?branch=master)](https://travis-ci.org/osorensen/hdme)
[![Codecov test coverage](https://codecov.io/gh/osorensen/hdme/branch/master/graph/badge.svg)](https://codecov.io/gh/osorensen/hdme?branch=master)
<!-- badges: end -->


The goal of hdme is to provide penalized regression methods for High-Dimensional Measurement Error problems (errors-in-variables).

## Installation

Install `hdme` from CRAN using.
```{r, eval=FALSE}
install.packages("hdme")
```

You can install the latest development version from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("osorensen/hdme", build_vignettes = TRUE)
```


## Methods
hdme provides implementations of the following algorithms:

The methods implemented in the package include

* Corrected Lasso for Linear Models (@loh2012)
* Corrected Lasso for Generalized Linear Models (@sorensen2015)
* Matrix Uncertainty Selector for Linear Models (@rosenbaum2010)
* Matrix Uncertainty Selector for Generalized Linear Models (@sorensen2018)
* Matrix Uncertainty Lasso for Generalized Linear Models (@sorensen2018)
* Generalized Dantzig Selector (@james2009)


## References
